\textbf{EECS 340: Assignment 3}

### 2020-02-20 assignment_3/article.tex
🐛 Fix conclusion typo in Question 1(a).

Now we have $f(n) = n = O(n^{(\log_a b) - \epsilon})$, where $0 < \epsilon = \log_a b - 1$, we can apply \textit{case 1} of the master theorem and conclude that the solution is $T(n) = \Theta(n)$.

>>>>

Now we have $f(n) = n = O(n^{(\log_a b) - \epsilon})$, where $0 < \epsilon = \log_a b - 1$, we can apply \textit{case 1} of the master theorem and conclude that the solution is $T(n) = \Theta(n^{\log_a b})$.
